---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EasyQualtrics

<!-- badges: start -->
<!-- badges: end -->

The goal of EasyQualtrics is to enable a user to import .csv files exported from Qualtrics into R and prepare those data sets for analysis with ease. 

## Installation

You can install the development version of EasyQualtrics from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ssusnea/EasyQualtrics")
```

## Importing a Qualtrics .csv

Given a file path for a .csv file, the `read_qualtrics` function imports the .csv and prepares it for data analysis and visualization. 

In the example below, the `file_path` variable is a stand in for a real file path provided by the user.

```{r example}
library(EasyQualtrics)

file_path <- fs::path_package("extdata", "qualtrics_ex_data.csv", package = "EasyQualtrics")

mydata <- read_qualtrics(file_path)
```

From there the user analyze, wrangle, or visualize their Qualtrics data as they would any other data set. 
