---
title: "Introduction to the Easy Qualtrics Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EasyQualtrics_Intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EasyQualtrics)
```

# EasyQualtrics

The `EasyQualtrics` package allows the user to import .csv files exported from Qualtrics into R by providing the file's path. 

In the example below, the variable `file_path` acts as a stand in for the file path the user would provide for the function `read_qualtrics()`. 

```{r example}
library(EasyQualtrics)

file_path <- fs::path_package("extdata", "qualtrics_ex_data.csv", package = "EasyQualtrics")

mydata <- read_qualtrics(file_path)
```
Calling `read_qualtrics()` will tidy the data frame provided by standardizing column names, removing unnecessary rows, and coercing the data frame's vectors into the appropriate classes. Most notably `read_qualtrics()` coerces certain vectors into likert vectors.

However the user should not blindly rely on this coercion as its success depends on the vector's elements matching Qualtric's default answer options and format. If even one element of the vector differs from Qualtric's default likert answers, `read_qualtrics()` will not coerce the vector into a likert vector. To prevent automatic likert coercion the user can set `read_qualtrics()`' `heuristics` argument to `FALSE`.

The final tidied data set is shown below. 

```{r}
head(mydata)
```

Qualtrics data frames imported using the `EasyQualtrics` package are unique because of their labels attribute. This attribute provides additional context for each column so that the user does not need to guess what question each column responds to. 

The user can freely subset their Qualtrics data frame while preserving the columns' labels. However the user should note that subsetting data frames of class `qualtrics` preserves the data frame's dimension.

```{r subsetting-examples}
subset_data <- mydata$status

subset_data2 <- mydata[, 1:4]

subset_data3 <- mydata[[2]]
```

Users can also perform all of the usual data analysis, wrangling, and cleaning that they would on any other data set. 

```{r}
library(ggplot2)
library(tidyverse)

mydata |> 
  select(marital, race) |> 
  filter(race == "American Indian or Alaska Native" | race == "Asian" | race == "Black or African American" | race == "Native Hawaiian or Other Pacific Islander" | race == "White") |> 
  ggplot(aes(x = marital, fill = race)) +
  geom_bar() +
  labs(title = "Division of Marital Status by Race", 
       x = "Marital Status",
       y = "Count",
       fill = "Race") + 
  scale_fill_brewer(palette = "Spectral") + 
  theme_minimal()
```

