---
title: "Introduction to the Easy Qualtrics Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EasyQualtrics_Intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EasyQualtrics)
```

# EasyQualtrics

The `EasyQualtrics` package allows the user to import .csv files exported from Qualtrics into R by providing the file's path. 

```{r example}
library(EasyQualtrics)

mydata <- read_qualtrics("~/Documents/EasyQualtrics/inst/extdata/qualtrics_ex_data.csv")
# this isn't the right file path!!! or the right way to do it! but it's just for now so I can continue writing the rest of it. 
# also this doesn't work because it's recursive???? that's what this error: "C stack usage  7973712 is too close to the limit" means.
```
Mention something about the likert conversion? 

```{r}
View(mydata)
```


Qualtrics data frames imported using the `EasyQualtrics` package are unique because of their labels attribute. This attribute provides additional context for each column so that the user does not need to guess what question a column is responding to. 

The user can freely subset their Qualtrics data frame while preserving the columns' labels.

```{r}
subset_data <- mydata$column
```

They can also perform all of the usual data analysis, wrangling, and cleaning that they would on any other data set. 

```{r}
# an example of plotting very simple information from the imported data set.
```

